\cvsection{Work Experience}

%% \begin{cventries}

  \cventry
  {HPC Systems Software Engineer}
  {National Energy Research Scientific Computing Center}
  {Lawrence Berkeley National Lab}
  {2024--present}
  {
    \begin{cvitems}
    \item{
      Responsible for developing, managing, and troubleshooting HPC cluster.
    }
    \item{
      Primary focus on NERSC's production system \textit{Perlmutter}:
      4864 compute nodes, 40 user login nodes, 30 DVS nodes, Lustre (ClusterStor), Ceph (Nexus), Slingshot network, Slurm scheduler, and Kubernetes-based system management (CSM)
    }
    \end{cvitems}
  }

  \cventry
  {Systems Engineer, Senior}  % Job title
  {Pixar Animation Studios}  % Organization
  {Emeryville/Remote}  % Location
  {2021--2024}  % Date(s)
  {
    \begin{cvitems}  % Description(s) of tasks/responsibilities
    \item{
      Responsible for Linux-based platform for compute farm and user workstations,
      including bare-metal servers, KVM hypervisors and guests, Nvidia Grid, Teradici, RHEL-based OS.
    }
    \item{Automate reporting to inform ongoing operations and structure future plans}
    %% \item mentor and train team members
    \item{Troubleshoot OS-level problems for Application Developers, QA, Support, Desktop}
    \end{cvitems}
  }

  \cventry
  {Systems Administrator, Senior}  % Job title
  %% {Pixar Animation Studios}  % Organization
  %% {Emeryville/Remote}  % Location
  {}
  {}
  {2018--2021}  % Date(s)
  {
    \begin{cvitems}  % Description(s) of tasks/responsibilities
    \item {Wrote tooling to compose, test, and deploy releases of RHEL-based OS runtime and Ansible-driven configuration}
    \item {Updated Linux workstation platform on regular schedule (\textasciitilde{}2200 hosts, 2x/month).}
    \end{cvitems}
  }

  \cventry
  {Systems Administrator}
  %% {Pixar Animation Studios}
  %% {Emeryville}
  {}
  {}
  {2014--2017}
  {
    \begin{cvitems}
    \item {Collaborated on design and implementation of virtualized, Teradici-connected Linux workstations.}
    \item {Worked with artists to solve usability issues during migration to remote platform.}
    \item {Ported in-house configuration management to Ansible}
    \end{cvitems}
  }

  \cventry
  {Production Support Engineer, Lead}
  %% {Pixar Animation Studios}
  %% {Emeryville}
  {}
  {}
  {2012--2014}
  {
    \begin{cvitems}
    \item {Advocated for production artists having problems with applications or systems infrastructure.}
    \item {Instituted queue reviews to encourage task completion and balance engineer workloads.}
    \item {Scripted common workarounds and automated configuration to reduce labor for common tasks.}
    \end{cvitems}
  }

  \cventry
  {Production Support Engineer}
  %% {Pixar Animation Studios}
  %% {Emeryville}
  {}
  {}
  {2008--2012}
  {
    \begin{cvitems}
    \item {Supported desktop Linux users, troubleshoot hardware, os, and application-level problems, escalating to other groups as needed.}
    \item {\textit{Keep animators animating.}}
    \end{cvitems}
  }

\vspace{\acvSectionContentTopSkip}
%% \end{cventries}
